Think deep for reef resilience

### 2025-08-12 paper/paper_draft.qmd
Expand on connectivity data/implementation caveats
@ConnectedSystems

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-----------------------|-----------------------|------------------------|-----------------------|
| ACCESS-CM2 | 4.66 [@grose2023]| High | **insert repo citation** |
| EC-Earth3-Veg | 4.30 [@wyser2020]| High | **insert repo citation** |
| GFDL-CM4 | 4.1 [@sentman2025]| High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 [@ziehn2020]| Intermediate | Main text |
| NorESM2-MM | 2.5 [@seland2020]| Low | **insert repo citation** |

@@

There are multiple caveats in how coral ecosystem dynamics are modelled in this
investigation. We model coral colonies as circular diameter values and track these diameters
over timesteps through growth. Due to the availability of quality future projected data we
do not consider the impacts of waves, cyclones, currents and Crown of Thorns Starfish (CoTS)
on coral colony survival and bleaching [@massel1993; @deaker2022]. Uncertainty in
connectivity modelling outputs, satellite-derived bathymetry data and future thermal stress
projections are likely to influence the results obtained in this investigation.
Incorporating further improvements in connectivity modelling and understanding of the
influence of climate change on reef connectivity would improve the comparison of
connectivity as an important factor for reef resilience. The DHW data used in this
investigation have not been bias corrected for the Great Barrier Reef region and are part of
a wider Australian dataset [@dixon2022] developed using statistical downscaling. We
investigate a range of future climate responses, thermal projections and ecological
parameterisations of ADRIA - CoralBlox to account for many possible futures, and our results
suggest the factors that influence reef resilience are consistent across these scenarios.

>>>>

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-----------------------|-----------------------|------------------------|-----------------------|
| ACCESS-CM2 | 4.66 [@grose2023] | High | **insert repo citation** |
| EC-Earth3-Veg | 4.30 [@wyser2020] | High | **insert repo citation** |
| GFDL-CM4 | 4.1 [@sentman2025] | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 [@ziehn2020] | Intermediate | Main text |
| NorESM2-MM | 2.5 [@seland2020] | Low | **insert repo citation** |

@@

There are multiple caveats in how coral ecosystem dynamics are modelled in this
investigation. We model coral colonies as circular diameter values that are tracked over
timesteps through growth. Due to the availability of quality future projected data we do not
consider the impacts of waves, cyclones, currents and Crown of Thorns Starfish (CoTS) on
coral colony survival and bleaching [@massel1993; @deaker2022]. Uncertainty in connectivity
modelling outputs, satellite-derived bathymetry data and future thermal stress projections
are likely to influence the results obtained in this investigation. While the resolution of
connectivity data used in this investigation improves upon data used in comparable studies
[@bozec2025], the time-mean implementation used may not effectively capture long term
patterns [@vogt-vincent2023]. Using alternative connectivity implementation methods that
better capture the ecological-timescale trends in reef connections rather than the high
daily variability, would improve confidence in the connectivity findings of this
investigation [@vogt-vincent2023]. The DHW data used in this investigation have not been
bias corrected for the Great Barrier Reef region and are part of a wider Australian dataset
[@dixon2022] developed using statistical downscaling. We investigate a range of future
climate responses, thermal projections and ecological parameterisations of ADRIA - CoralBlox
to account for many possible futures, and our results suggest the factors that influence
reef resilience are consistent across these scenarios.
